IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-07-08 paper/retrofit.tex
typo

While this is a very simple example, we can still ask: given the
obviously safe formulation with separate heaps, can this fact be useful
for showing the safety of an semantics which only has a single heap
(Yes: see Section~\ref{sec:single-heap})?  Furthermore, the ``raw''
semantics violates expectations about how inter-thread communication
works on a shared heap: it strongly suggests, for example, that which
types of data may be passed between tasks should be restricted (for
example, in JavaScript, one might only allow JSON objects to be passed
between tasks).

>>>>

While this is a very simple example, we can still ask: given the
obviously safe formulation with separate heaps, can this fact be useful
for showing the safety of a semantics which only has a single heap
(Yes: see Section~\ref{sec:single-heap})?  Furthermore, the ``raw''
semantics violates expectations about how inter-thread communication
works on a shared heap: it strongly suggests, for example, that which
types of data may be passed between tasks should be restricted (for
example, in JavaScript, one might only allow JSON objects to be passed
between tasks).
